Plot curve fits

### 2023-01-30 Working Rmds/plot_fits.Rmd
Evaluating residuals by RMSE, R-squared, and overall error SD. Evaluating TK stats by tmax, Cmax, AUC. All evaluations under combinations of the following fitting conditions: log-transform TRUE/FALSE, dose-normalization TRUE/FALSE, rescale time TRUE/FALSE. Residuals for each fitting condition also calculated in all of the following combinations: log-scale residuals TRUE/FALSE, dose-normalized residuals TRUE/FALSE. This way we can compare apples to apples.

```{r}
timestamp <- "2023_01_17"
```

@@

```{r, load_cvt, eval = TRUE}
cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
"2023_01_13",
".csv"))
cvt[, Reference:=as.character(Reference)]
cvt[, Reference_orig:=as.character(Reference_orig)]
```

Read in the fitted model parameter values.

```{r, read_data}

fit_1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
fit_2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
fit_flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))

#pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
```

Plot concentration vs time with the best-fit params by data subset (DTXSID and species).

Indicate the following:

- One line for each model
- Which is the winning model
- Dose group
- Blood vs. plasma
- Below LOQ vs. above LOQ (plot below-LOQ points at LOQ)
- IV vs. oral administration

Plot all models together for the joint analysis.

Produce a data.table with unique combinations of DTXSID, species, analysis type, and studies analyzed.

```{r}
plot_combos <- unique(fit_flat[Analysis_Type %in% "Joint", .(Analysis_Type,
                                                             DTXSID,
                                                             Species,
                                                             Studies.Analyzed)])
setnames(plot_combos,
         names(plot_combos),
         paste(names(plot_combos),
               "in",
               sep = "_"))
```

Loop over the following combinations of options:
- Log-scale y and non-log-scale y
- Dose-normalized and split-dose

```{r}
opts_DT <- as.data.table(expand.grid(log10_scale_y = c(TRUE, FALSE),
                       split_dose = c(TRUE, FALSE)))
opts_DT[, plot_errbars := !(log10_scale_y)]
opts_DT[, plot_dose_norm := !(split_dose)]
opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% TRUE,
        file_suffix := "errbars_naturaly_dose_norm"]
opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% TRUE,
        file_path := "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_norm"]
opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% TRUE,
        file_suffix := "noerrbars_logy_dose_norm"]
opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% TRUE,
        file_path := "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_norm"]

opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% FALSE,
        file_suffix := "errbars_naturaly_dose_split"]
opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% FALSE,
        file_path := "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_split"]
opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% FALSE,
        file_suffix := "noerrbars_logy_dose_split"]
opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% FALSE,
        file_path := "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_split"]
```

Loop over options, and within each option, loop over datasets, to plot joint analysis with all models.
```{r}
junk <- mapply(function(plot_errbars,
                       log10_scale_y,
                       plot_dose_norm,
                       split_dose,
                       file_suffix,
                       file_path){
  print(file_suffix)
DT_plot <- plot_combos[,
                       .(plot_obj = list(
                         {
                          studies_list <- strsplit(Studies.Analyzed_in,
                               split = ", ")[[1]]
      #get data.table of newdata to be predicted
      #leave out DTXSID, Species columns
      #since these will be added back in from fit_combs
      obs_data <- cvt[DTXSID %in% DTXSID_in &
                           Species %in% Species_in &
                           Study %in% studies_list]

      plot_fit(fit_flat = fit_flat,
               fit_1comp = fit_1comp,
               fit_2comp = fit_2comp,
               DTXSID_in = DTXSID_in,
                 Species_in = Species_in,
                 obs_data = obs_data,
                 model_in = "all",
                 Analysis_Type_in = "Joint",
                 plot_dose_norm = plot_dose_norm,
                 split_dose = split_dose,
                 n_interp_time = 10,
                     limit_y_axis = FALSE,
                     log10_scale_y = log10_scale_y,
                     plot_errbars = plot_errbars,
                     log10_scale_time = FALSE,
                 return_plot = TRUE,
                 save_plot = TRUE,
                 file_suffix = file_suffix,
                     file_path = file_path,
                 verbose = FALSE,
                 ggsave_args = list(scale = 1,
                                        width = 13.33,
                                        height = 7.5,
                                        units = "in",
                                        dpi = 300,
                                        limitsize = TRUE,
                                        bg = NULL)
                 )
                       })),
        by = .(DTXSID_in,
               Species_in,
               Analysis_Type_in,
               Studies.Analyzed_in)]

#save all plots as one big paginated file
pdf(paste0(file_path,
              "/all_plots_",
              file_suffix,
              ".pdf"),
    width = 13.33,
                                        height = 7.5)
print(DT_plot$plot_obj)
dev.off()

rm(DT_plot)

return(0)
},
plot_errbars = opts_DT$plot_errbars,
                       log10_scale_y = opts_DT$log10_scale_y,
                       plot_dose_norm = opts_DT$plot_dose_norm,
                       split_dose = opts_DT$split_dose,
file_suffix = opts_DT$file_suffix,
file_path = opts_DT$file_path)

```

>>>>

```{r}
timestamp <- "2023_01_23"
```

@@

```{r, load_cvt, eval = TRUE}
cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
timestamp,
".csv"))
cvt[, Reference:=as.character(Reference)]
cvt[, Reference_orig:=as.character(Reference_orig)]
```

# Plot fits for each combination of fitting & plotting options

```{r}
for(rescale_time in c(FALSE, TRUE)){
  for(fit_conc_dose in c(FALSE, TRUE)){
    for(fit_log_conc in c(FALSE, TRUE)){
      #get fitting outputs file names
      fit_outputs <- dir(path = "../inst/ext",
                         pattern = paste0("PK_fit_table_",
                                          ".+",
                                          "_fit_log_conc_",
                                          fit_log_conc, "_",
                                          "_fit_conc_dose_",
                                          fit_conc_dose, "_",
                                          "_rescale_time_",
                                          rescale_time, "_"
                         ))

      fit_outputs <- paste0("../inst/ext/",
                            fit_outputs)

      cat(paste0(paste(fit_outputs,
                       collapse = "\n"), "\n"))

      #read in fitting outputs
      #flat model
      fit_flat <- fread(grep(x = fit_outputs,
                             pattern = "flat",
                             value = TRUE))
      #1compartment model
      fit_1comp <- fread(grep(x = fit_outputs,
                              pattern = "1compartment",
                              value = TRUE))
      #2compartment model
      fit_2comp <- fread(grep(x = fit_outputs,
                              pattern = "2compartment",
                              value = TRUE))
      #add in fitting options
      fit_flat[, c("fit_conc_dose",
                   "fit_log_conc",
                   "rescale_time") := .(fit_conc_dose,
                                        fit_log_conc,
                                        rescale_time)]

      fit_1comp[, c("fit_conc_dose",
                    "fit_log_conc",
                    "rescale_time") := .(fit_conc_dose,
                                         fit_log_conc,
                                         rescale_time)]

      fit_2comp[, c("fit_conc_dose",
                    "fit_log_conc",
                    "rescale_time") := .(fit_conc_dose,
                                         fit_log_conc,
                                         rescale_time)]

      #get unique combinations of DTXSID, Species, Analysis_Type, Studies. Analyzed
      plot_combos <- unique(
        fit_flat[Analysis_Type %in% "Joint",
                 .(Analysis_Type,
                   DTXSID,
                   Species,
                   Studies.Analyzed)])
      setnames(plot_combos,
               names(plot_combos),
               paste(names(plot_combos),
                     "in",
                     sep = "_"))

      #now, loop over plotting options:
      #plot log-scale, plot dose-normalized

      for(log10_scale_y in c(TRUE, FALSE)){
        for(plot_dose_norm in c(TRUE, FALSE)){
          cat(paste0("rescale_time = ", rescale_time,"\n",
                     "fit_conc_dose = ", fit_conc_dose,"\n",
                     "fit_log_conc = ", fit_log_conc,"\n",
                     "log10_scale_y = ", log10_scale_y,"\n",
                     "plot_dose_norm = ", plot_dose_norm,"\n"))
          #for each row of plot_combos, create a plot
          DT_plot <- plot_combos[,
                                 .(plot_obj = list(
                                   {
                                     studies_list <- strsplit(Studies.Analyzed_in,
                                                              split = ", ")[[1]]
                                     #get data.table of newdata to be predicted
                                     #leave out DTXSID, Species columns
                                     #since these will be added back in from fit_combs
                                     obs_data <- cvt[DTXSID %in% DTXSID_in &
                                                       Species %in% Species_in &
                                                       Study %in% studies_list]

                                     plot_fit(fit_flat = fit_flat,
                                              fit_1comp = fit_1comp,
                                              fit_2comp = fit_2comp,
                                              DTXSID_in = DTXSID_in,
                                              Species_in = Species_in,
                                              obs_data = obs_data,
                                              model_in = "all",
                                               fit_log_conc = fit_log_conc,
                     fit_conc_dose = fit_conc_dose,
                     rescale_time = rescale_time,
                                              Analysis_Type_in = "Joint",
                                              plot_dose_norm = plot_dose_norm,
                                              split_dose = (!plot_dose_norm),
                                              n_interp_time = 10,
                                              limit_y_axis = FALSE,
                                              log10_scale_y = log10_scale_y,
                                              plot_errbars = (!log10_scale_y),
                                              log10_scale_time = FALSE,
                                              return_plot = TRUE,
                                              save_plot = FALSE,
                                              file_suffix = NULL,
                                              file_path = NULL,
                                              verbose = FALSE
                                     )
                                   }
                                 )
                                 ),
                                 by = .(DTXSID_in,
                                        Species_in,
                                        Analysis_Type_in,
                                        Studies.Analyzed_in)]

          #save all plots as one big paginated file
          pdf(paste0("../inst/ext/plots/",
                     "plots_",
                     "fit_log_conc_",
                     fit_log_conc, "_",
                     "fit_conc_dose_",
                     fit_conc_dose, "_",
                     "rescale_time_",
                     rescale_time, "_",
                     "plotlog10y_", log10_scale_y, "_",
                     "plotdosenorm_", plot_dose_norm,
                     ".pdf"),
              width = 13.33,
              height = 7.5)
          print(DT_plot$plot_obj)
          dev.off()
        } #end for plot_dose_norm
      }#end for log10_scale_y
    } #end for fit_log_conc
  }#end for fit_dose_norm
}#end for rescale_time
```

Tradeoffs I notice:

Fitting on the log scale gives a better fit to late elimination-phase points, sometimes at the expense of underpredicting Cmax. Solvent red 1 (DTXSID3061635) is a prime example. This happens because log-transforming observations before fitting tends to increase the scale of errors for points with small observed concentrations, and tends to decrease the scale of errors for points with large observed concentrations.

This effect is stronger if the range of observed concentrations is more than one order of magnitude. For example, for solvent red 1, concentrations range from about 0.05 down to about 1e-4. When fit on the natural scale, the 1-compartment model wins, because it fits the peak better. When fit on the log scale, the 2-compartment model wins, because it fits the tail better.

Trichloroethylene (in rat) is another interesting case. When fitted on the natural scale without dose normalization, the 7.6 mg/kg dose is fitted well, but the 18 mg/kg dose is fitted poorly (underpredicted), and the 1-compartment model wins. When fitted on the log scale without dose normalization, the 18 mg/kg dose is fitted better, at the expense of overpredicting the 7.6 mg/kg dose, and the 2-compartment model wins. I'm not sure why the 18 mg/kg dose is underpredicted on the natural scale without dose normalization; the scale of the errors should be higher for the peak there.

Questions we want to ask:

- Does error vary by dose?
- Does error vary by time (absorption, elimination phases)?
- How well do we predict Cmax on a non-dose-normalized basis?
- How well do we predict Cmax on a dose-normalized basis?
- How well do we predict tmax?
- How well do we predict AUC infinity?

Probably we should do something like assess percentage error (error as a percentage of observed value). That corresponds to, roughly, the visual difference between fitted curves and observed points on the split-dose plots.
